---
title: Women's autonomy in decision making
author: ''
date: '2019-09-29'
slug: women-autonomy-in-decision-making
categories:
  - publicdata
tags:
  - datavis
  - tidyverse
  - tutorial
cover: ''
description: 'Blah'
keywords:
  - 'tutorial'
  - 'public dataset'
  - 'tidyverse'
  - 'ggplot'
showFullContent: no
---

After travelling in the past few weekends, I finally found some time to look at some potentially interesting data provided by <a href = 'https://data.worldbank.org/indicator/SG.DMK.ALLD.FN.ZS'> The World Bank </a>. 

**World Bank estimated scores for women participating in three major decisions: own healthcare, major household purchases and visiting family**. I wanted to see how the trend on these has changed over time/which countries have highest & lowest score.

I started the work by reading in the data using `readr`. After downloading and unzipping the files, I placed them inside "data" folder in my repo:

```{r path, results="hide"}
path <- '../women-making-decisions/data/' 

```
There are several files in the folder (3 files are downloaded automatically), and their names are tedious, so I wanted to do it in several steps:

- Step 1: find all files in the folder (the path folder we just saved into R)
- Step 2: select the one we want

My original code does exactly that:

```{r original_code, eval=FALSE}
file_list <- list.files(path="data/")

df <- readr::read_csv(paste0('data/', file_list[1]), skip = 3)

df_additional_1 <-readr::read_csv(paste0('data/', file_list[2]))
df_additional_2 <-readr::read_csv(paste0('data/', file_list[3]))

```


But, turns out, R markdown *really* doesn't like it when we try to list files in another repo. There's a reported reproducible bug that I found, so maybe one day :) . Therefore, this is the code for you if you want to follow along this tutorial:




